### 2015-07-20 implementation-environment.tex
Name change spack-paper-sc15 -> spack-sc15
Updated wrapper overhead figure

>>>>

\begin{figure}
	\centering
	\includegraphics[width=\columnwidth]{figs/wrappers/wrapper-overhead.pdf}
	\caption{
		Build times with and without Spack's compiler wrappers.
		\label{fig:wrapper-overhead}
	}
\end{figure}

Spack's compiler wrappers incur a small amount of overhead because they intercept
calls to compilers within a build.  Figure~\ref{fig:wrapper-overhead} shows build time
with and without the wrappers for seven different packages.
